
\section{Installing JDK}

If you have the latest JDK 6 installed\footnote{You should check out the latest
version at
\url{http://www.oracle.com/technetwork/java/javase/downloads/index.html} as the
version number grows really fast}, you could skip this task.

We assume you have experience in Java programming, but we still need to clarify
the Java environment for the course. If you don't have any Java experience,
probably you need to look for a Java textbook. It might also be fine if you
think you have tons of experience in programming in C++/C\# and you feel
confident to learn Java by just reading others' codes and guessing their
meanings. It's up to you!

\begin{enumerate}

\item Visit
\url{http://www.oracle.com/technetwork/java/javase/downloads/index.html}, and
choose the platform you are using to download JDK 6 SE 35\footnote{By the date
of August 31, 2012}.

\begin{qa}

\item[Q1] Can I just install JRE instead of JDK?

\item[A1] No.

\item[Q2] Can I install OpenJDK instead of SunJDK (or OracleJDK)?

\item[A2] Sure, you can. But be aware that sometimes only binary files (aka JRE)
are installed under a folder named \texttt{openjdk-\emph{version}}, rather than
\texttt{openjre-\emph{version}}, which is a bit confusing.

\item[Q3] Can I install JDK 7, 5 or older versions?

\item[A3] You are not recommended to install JDK 7, since you have to modify the
Maven pom file to compile your project, and the cluster that we will run and
test your components does not have JDK 7 set up yet. But it would be fine
(theoretically) if you have just JDK 5 installed, but it is still not
recommended. Versions older than 5 should be completely avoided.

\item[Q4] Can I use an earlier version of JDK 6 (e.g., 6u4)?

\item[A4] It may not put you in a trouble most of time, but in some rare cases,
we did find an exception was thrown due to a bug not in our code but in the
runtime environment. Therefore, we recommend you to upgrade your JDK 6 to the
latest version.

\end{qa}

\item Install JDK from the executable file if available, and set PATH manually
(if you are using a Windows machine). The Java installation page (at
\url{http://www.oracle.com/technetwork/java/javase/index-137561.html}) might be
useful to you.

\end{enumerate}