% 
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0
% Unported License. To view a copy of this license, visit
% http://creativecommons.org/licenses/by-sa/3.0/.
%
% author: Zi Yang <ziy@cs.cmu.edu>
% date: 09/02/2012
%
\documentclass[oneside]{memoir}

\renewcommand{\chaptername}{Task}

\usepackage{times}

\usepackage{titlesec}
\titleformat{\section}{\normalfont\Large\bfseries}{Task \thesection}{1em}{}

\usepackage{url}
\usepackage{hyperref}

\usepackage{graphicx}
\graphicspath{{../../fig/uml-and-uima/}}

\usepackage{pstricks}
\usepackage{epsfig}

\usepackage{listings}
\usepackage{color}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{lightblue}{rgb}{0.95,0.95,1}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\lstset{
  basicstyle=\ttfamily\small,
  numbers=left,
  numberstyle=\tiny\color{gray},
  stepnumber=2, 
  numbersep=5pt,
  backgroundcolor=\color{lightblue},
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  frame=lines,
  rulecolor=\color{black},
  tabsize=2,
  captionpos=b,
  breaklines=true,
  breakatwhitespace=false,
  title=\lstname,
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  escapeinside={\%*}{*)},
  morekeywords={*,...},
}
\usepackage{letltxmacro}
\makeatletter
\LetLtxMacro\@@lst@inputlisting\lst@inputlisting
\renewcommand\lst@inputlisting[2][]{%
  \try@listingspath{#2}%
  \if@tempswa
    \typeout{Using \@foundlisting}%
    \@@lst@inputlisting[#1]{\@foundlisting}%
  \else
    \typeout{Missing file #2}\endgroup
  \fi}
\def\listingspath#1{\def\@listingspath{#1}}
\listingspath{}
\def\try@listingspath#1{%
  \@tempswafalse
  \expandafter\@tfor\expandafter\next
  \expandafter:\expandafter=\@listingspath\do
  {\if@tempswa\@break@tfor\fi
   \IfFileExists{\next/#1}{\@tempswatrue\xdef\@foundlisting{\next/#1}}{}}%
}
\makeatletter
\listingspath{{../../lst/uml-and-uima/}}

\definecolor{shadecolor}{gray}{0.9}

\newenvironment{qa}
{\begin{shaded}\begin{itemize}}
{\end{itemize}\end{shaded}}

\title{{\bfseries 11-791 Design and Engineering of Intelligent Information
System Fall 2012\\Homework 1}\\
\vspace{1em}
\itshape\rmfamily UML Design and Named Entity Recognition Implementation with
UIMA SDK}

\date{}

\begin{document}

\begin{titlingpage}
\maketitle

\hspace{-0.1\textwidth}
\begin{minipage}{1.2\textwidth}
\vspace{-5em}
\textbf{Important dates}
\begin{itemize}

\item \textbf{Hand out: October 2.}\footnote{This version was built on September
28, 2012}

\item \textbf{Turn in: October 16.} Besides all your Java source codes, and UIMA
type system, collection reader and analysis engine descriptors, which are
essential to your UIMA collection processing engine, you are also required to
answer UML design related questions, write a report for your implementation of
the named entity recognizer, and include the Javadocs.

If you have ever looked into your \verb|target/| directory or Maven
course-release repository for Homework 0, then you will find that Maven will
package the binary files, source files, and Javadocs into different jars, and
deploy them on the server, which means all you need to do is to put all the
source codes and descriptors, as well as the documents, in the right place of
your hw1-ID project. You should organize your project in the same hierarchy as
shown below\footnote{To simplify your submission process and our evaluation
process, we ask you to create \texttt{src/main/resources/docs} for your
documents. But you should keep in mind it is NOT a good practise to have
documentation within a \texttt{src} folder.}:

\small
\begin{verbatim}
hw1-ID
|- pom.xml
`- src
     `- main
        |- java
      |   `- **/*.java            /* your Java codes go into this folder 
      |                           * as you did before */
        `- resources
         |- CpeDescriptor.xml    /* the entry point for your cpe */
         |- **/*.xml             /* all your descriptors go into the 
         |                        * resources folder */
         `- docs
            |- hw1-ID-uml.pdf    /* your UML design writeup */
            `- hw1-ID-report.pdf /* your report for the pipeline */

\end{verbatim}
\normalsize

\end{itemize}

\end{minipage}
\hspace{-0.1\textwidth}

\hspace{-0.1\textwidth}
\begin{minipage}{1.2\textwidth}

Several notes about organizing your Maven project and other additional
information:

\begin{enumerate}

\item \textbf{Submission:} The same way as you did for Homework 0 (set up GitHub
repo, create Maven project, write your code, submit to Maven repo), except that
the name has changed to hw1-ID.

\item \textbf{Your source files and descriptors:} \verb|**/*.java| and
\verb|**/*.xml| tell you that you don't need to flatten your folder hierarchy,
instead we encourage you to place your Java codes in the right package, and
similarly, you can create subfolders for different types of descriptors, e.g.,
\verb|src\main\resources\descriptors\ner| for all the analysis engine
descriptors related to named entity recognition task. We will look into your jar
packages.

One very special descriptor is the \verb|CpeDescriptor.xml|, which is the entry
point for the entire pipeline. You are required to name your CPE descriptor
exactly the same way, and place it in the right place for us to evaluate your
code.

\item \textbf{UML design answers and report:} We will pull out your documents
from your jar files, and Prof. Eric Nyberg will look into your report and
answers for the questions, so that remember to include your ID as part of file
names, and put your name and ID in your document. You can submit either PDF
files or DOC/DOCX files (hw1-ID-uml.doc or .docx in the latter case).

\item \textbf{Javadocs:} Please refer to any best practise (yes, there might be
more than one) to write your Javadoc, e.g.,
\url{http://www.oracle.com/technetwork/java/javase/documentation/index-137868.html}.
We expect you to describe your major components at the class level of your
Javadoc, and put additional comments on the most important methods if any. It
might be a good idea to include your UML design in your Javadoc if you think the
developers can have a general idea by just looking at your diagram.

\item \textbf{Performance evaluation:} We believe you may have different ideas
about how to design the type system, and how to implement a name entity
recognizer, which means we won't prepare a shared type system for you to build
components on (but we will have one in Homework 2). Therefore, you are required
to write a collection reader to load the input text and a CAS consumer to
generate your output (both are independent of your specific type system), and
our evaluation will based on the output from your CAS consumer, similar as we
did for Homework 0.

\end{enumerate}

\textbf{Useful information}
\begin{enumerate}
\item We encourage you to start Homework 1 as early as possible, especially if
you haven't gotten a chance to browse the UIMA portal.

\item For any question regarding the UML design part of Homework 1, please send
mails directly to Prof. Eric Nyberg
(\href{mailto:ehn@cs.cmu.edu}{\nolinkurl{ehn@cs.cmu.edu}}), and for other
questions, please send us mails: Zi Yang
(\href{mailto:ziy@cs.cmu.edu}{\nolinkurl{ziy@cs.cmu.edu}}) or Rui Liu
(\href{mailto:ruil@cs.cmu.edu}{\nolinkurl{ruil@cs.cmu.edu}}).

\item Again, both source files and pdf file of this assignment are
publicly available on my GitHub

\url{http://github.com/ziy/software-engineering-preliminary}

Please feel free to fork the project and send a pull request back to me as some
of you did for Homework 0 for any error. Or you can just report an issue at

\url{http://github.com/ziy/software-engineering-preliminary/issues}

\end{enumerate}

\end{minipage}
\hspace{-0.1\textwidth}

\end{titlingpage}

\input{uml/intro}

\input{ner/intro}

\input{uima/intro}

\input{appendix}

\end{document}
