% 
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0
% Unported License. To view a copy of this license, visit
% http://creativecommons.org/licenses/by-sa/3.0/.
%
% author: Zi Yang <ziy@cs.cmu.edu>
% date: 09/02/2012
%
\documentclass[oneside]{memoir}



\renewcommand{\chaptername}{Task}

\usepackage{times}

\usepackage{titlesec}
\titleformat{\section}{\normalfont\Large\bfseries}{Task \thesection}{1em}{}

\usepackage{url}
\usepackage{hyperref}

\usepackage{graphicx}
\graphicspath{{../../fig/uml-and-uima/}}

\usepackage{pstricks}
\usepackage{epsfig}

\usepackage{listings}
\usepackage{color}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{lightblue}{rgb}{0.95,0.95,1}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\lstset{
  basicstyle=\ttfamily\small,
  numbers=left,
  numberstyle=\tiny\color{gray},
  stepnumber=2, 
  numbersep=5pt,
  backgroundcolor=\color{lightblue},
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  frame=lines,
  rulecolor=\color{black},
  tabsize=2,
  captionpos=b,
  breaklines=true,
  breakatwhitespace=false,
  title=\lstname,
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  escapeinside={\%*}{*)},
  morekeywords={*,...},
}
\usepackage{letltxmacro}
\makeatletter
\LetLtxMacro\@@lst@inputlisting\lst@inputlisting
\renewcommand\lst@inputlisting[2][]{%
  \try@listingspath{#2}%
  \if@tempswa
    \typeout{Using \@foundlisting}%
    \@@lst@inputlisting[#1]{\@foundlisting}%
  \else
    \typeout{Missing file #2}\endgroup
  \fi}
\def\listingspath#1{\def\@listingspath{#1}}
\listingspath{}
\def\try@listingspath#1{%
  \@tempswafalse
  \expandafter\@tfor\expandafter\next
  \expandafter:\expandafter=\@listingspath\do
  {\if@tempswa\@break@tfor\fi
   \IfFileExists{\next/#1}{\@tempswatrue\xdef\@foundlisting{\next/#1}}{}}%
}
\makeatletter
\listingspath{{../../lst/uml-and-uima/}}

\usepackage{multirow}

\definecolor{shadecolor}{gray}{0.9}

\newenvironment{qa}
{\begin{shaded}\begin{itemize}}
{\end{itemize}\end{shaded}}

\title{{\bfseries 11-791 Design and Engineering of Intelligent Information
System \& \\11-693 Software Methods for Biotechnology \\Homework 1}\\
\vspace{1em}
\itshape\rmfamily Logical Data Model and UIMA Type System Design \&
Implementation}

\date{}

\begin{document}

\begin{titlingpage}
\maketitle

\hspace{-0.1\textwidth}
\begin{minipage}{1.2\textwidth}
\vspace{-5em}
\textbf{Important dates}
\begin{itemize}

\item \textbf{Hand out: September 4.}\footnote{This version was built on \today}

\item \textbf{Turn in: September 11.} In this homework, you will create a
logical data model for a sample information processing task. Based on your
analysis of the requirements, you will need to submit a report to describe how
you design an appropriate UIMA type system to model the required information
types. Then, you will use the UIMA tooling in Eclipse to create a type system
\verb|.xml| file; use the \texttt{JCasGen} plugin to compile your type system
into Java type classes.

If you have ever looked into your \verb|target/| directory or Maven
course-release repository for Homework 0, then you will find that Maven will
package the binary files, source files, and Javadocs into different jars, and
deploy them on the server, which means all you need to do is to put all the
source codes and descriptors, as well as the documents, in the right place of
your hw1-ID project. You should organize your project in the same hierarchy as
shown below\footnote{To simplify your submission process and our evaluation
process, we ask you to create \texttt{src/main/resources/docs} for your
documents. But you should keep in mind it is NOT a good practise to have
documentation within a \texttt{src} folder.}:

\small
\begin{verbatim}
hw1-ID
|- pom.xml
`- src
     `- main
        |- java
      |   `- **/*.java      /* Java classes generated by JCasGen */ 
        `- resources
         |- hw1-ID-typesystem.xml /* your type system */
         |- **/*.*                /* (optional) other resources */
         `- docs
            `- hw1-ID-report.pdf  /* your report for design */

\end{verbatim}
\normalsize

\end{itemize}

\end{minipage}
\hspace{-0.1\textwidth}

\hspace{-0.1\textwidth}
\begin{minipage}{1.2\textwidth}

Several notes about organizing your Maven project and other additional
information:

\begin{enumerate}

\item \textbf{Submission:} The same way as you did for Homework 0 (set up GitHub
repo, create Maven project, write your code, submit to Maven repo), except that
the name has changed to hw1-ID.

\item \textbf{Your source files and type system descriptor(s):} \verb|**/*.java|
and \verb|**/*.*| tell you that you don't need to flatten your folder hierarchy,
instead we encourage you to place your Java codes in the right package by
specifying the right package name for each type you defined in the
\verb|hw1-ID-typesystem.xml| file. You can also create sub type systems and
import them into your main type system. We will look into your jar packages.

\item \textbf{Your report for design:} We expect to see your requirement
analysis for the sample information system in your report. We will pull out your
documents from your jar files. Remember to include your ID as part of file
names, and put your name and ID in your document. Please submit in PDF format
only. If you think it might be easier to describe your design with a UML
diagram, you can optionally put one in your report.

\item \textbf{Javadocs:} Please remember to give an appropriate description for
each type you create and feature you add, which will end up being the Java
comments in the Java classes generated by the \texttt{JCasGen}. You might want
to refer to any best practise (yes, there might be more than one) to write your
Javadoc, e.g.,
\url{http://www.oracle.com/technetwork/java/javase/documentation/index-137868.html}.
We expect you to describe your major components at the class level of your
Javadoc, and put additional comments on the most important methods if any.

\end{enumerate}

\textbf{Useful information}
\begin{enumerate}
\item We encourage you to start Homework 1 as early as possible, especially if
you haven't got a chance to browse the UIMA portal.

\item Please post your questions regarding Homework 1 on Piazza
\url{https://piazza.com/cmu/fall2013/11791}. For other issues or concenrs, you
can also send us mails to, Alkesh Patel
(\href{mailto:alkeshku@andrew.cmu.edu}{\nolinkurl{alkeshku@andrew.cmu.edu}}), Di
Wang (\href{mailto:diwang@cs.cmu.edu}{\nolinkurl{diwang@cs.cmu.edu}}), or Zi
Yang (\href{mailto:ziy@cs.cmu.edu}{\nolinkurl{ziy@cs.cmu.edu}}).

\item Again, both source files and pdf file of this assignment are
publicly available on my GitHub

\url{http://github.com/ziy/software-engineering-preliminary}

Please feel free to fork the project and send a pull request back to me as some
of you did for Homework 0 for any error. Or you can just report an issue at

\url{http://github.com/ziy/software-engineering-preliminary/issues}

\end{enumerate}

\end{minipage}
\hspace{-0.1\textwidth}

\end{titlingpage}

\input{task/intro}

\input{uima/intro}

\input{appendix/intro}

\end{document}
