\documentclass[oneside]{memoir}

\renewcommand{\chaptername}{Task}

\usepackage{times}

\usepackage{titlesec}
\titleformat{\section}{\normalfont\Large\bfseries}{Task \thesection}{1em}{}

\usepackage{url}
\usepackage{hyperref}

\usepackage{graphicx}
\graphicspath{{../../fig/uml-and-uima/}}

\usepackage{pstricks}
\usepackage{epsfig}

\usepackage{listings}
\usepackage{color}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{lightblue}{rgb}{0.95,0.95,1}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\lstset{
  basicstyle=\ttfamily\small,
  numbers=left,
  numberstyle=\tiny\color{gray},
  stepnumber=2, 
  numbersep=5pt,
  backgroundcolor=\color{lightblue},
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  frame=lines,
  rulecolor=\color{black},
  tabsize=2,
  captionpos=b,
  breaklines=true,
  breakatwhitespace=false,
  title=\lstname,
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  escapeinside={\%*}{*)},
  morekeywords={*,...},
}
\usepackage{letltxmacro}
\makeatletter
\LetLtxMacro\@@lst@inputlisting\lst@inputlisting
\renewcommand\lst@inputlisting[2][]{%
  \try@listingspath{#2}%
  \if@tempswa
    \typeout{Using \@foundlisting}%
    \@@lst@inputlisting[#1]{\@foundlisting}%
  \else
    \typeout{Missing file #2}\endgroup
  \fi}
\def\listingspath#1{\def\@listingspath{#1}}
\listingspath{}
\def\try@listingspath#1{%
  \@tempswafalse
  \expandafter\@tfor\expandafter\next
  \expandafter:\expandafter=\@listingspath\do
  {\if@tempswa\@break@tfor\fi
   \IfFileExists{\next/#1}{\@tempswatrue\xdef\@foundlisting{\next/#1}}{}}%
}
\makeatletter
\listingspath{{../../lst/uml-and-uima/}}

\usepackage{multirow}

\definecolor{shadecolor}{gray}{0.9}

\newenvironment{qa}
{\begin{shaded}\begin{itemize}}
{\end{itemize}\end{shaded}}

\title{{\bfseries 11-791 Design and Engineering of Intelligent Information
System \& \\11-693 Software Methods for Biotechnology \\Homework 3}\\
\vspace{1em}
\itshape\rmfamily 
Execution Architecture with CPE and Deployment Architecture with UIMA-AS}

\date{}

\begin{document}

\begin{titlingpage}
\maketitle

\hspace{-0.1\textwidth}
\begin{minipage}{1.2\textwidth}
\vspace{-5em}
\textbf{Important dates}
\begin{itemize}

\item \textbf{Hand out: September 24.}\footnote{This version was built on \today}

\item \textbf{Turn in: Octpber 2.} In this homework, you will excute your pipeline of homework 2
with CPE and deploy it as service with UIMA-AS. 
You should organize your project in the same
hierarchy as shown below:

\small
\begin{verbatim}
hw3-ID
|- pom.xml
`- src
     `- main
        |- java
      |   `- **/*.java      /* Java classes generated by JCasGen
      |                        and your UIMA annotators         */ 
        `- resources
         |- hw2-ID-aae.xml        /* your aggregate analysis engine of homework 2*/
         |- hw2-ID-aae-client.xml /* clinet descriptor of your AAE */
         |- hw2-ID-aae-deploy.xml /* deployment descriptor of your AAE */
         |- hw3-ID-aae-as-CPE.xml /* CPE descriptor to test your AAE service */
         |- hw3-ID-CPE.xml        /* CPE descriptor of your homework 2 pipeline */
         |- scnlp-ID-client.xml   /* clinet descriptor for the remote UIMA-AS service */
         |- **/*.*                /* analysis engine and other resources */
         `- docs
            `- hw3-ID-report.pdf  /* your report for design */

\end{verbatim}
\normalsize

\end{itemize}

\end{minipage}
\hspace{-0.1\textwidth}

\hspace{-0.1\textwidth}
\begin{minipage}{1.2\textwidth}

Several notes about organizing your Maven project and other additional
information:

\begin{enumerate}

\item \textbf{Submission:} The same way as you did for Homework 0, 1 and 2 (set up
GitHub repo, create Maven project, write your code, submit to Maven repo),
except that the name has changed to hw3-ID.

\item \textbf{Your report for design:} We expect to see how you design the
execution and deployment architecture for the sample information system in your report. We will
pull out your documents from your jar files. Remember to include your ID as part
of file names, and put your name and ID in your document. Please submit in PDF
format only.

\item \textbf{Javadocs:} Please remember to give an appropriate description for
each annotator you create.

\item Please post your questions regarding Homework 3 on Piazza
\url{https://piazza.com/cmu/fall2013/11791}. For other issues or concenrs, you
can also send us mails to, Alkesh Patel
(\href{mailto:alkeshku@andrew.cmu.edu}{\nolinkurl{alkeshku@andrew.cmu.edu}}), Di
Wang (\href{mailto:diwang@cs.cmu.edu}{\nolinkurl{diwang@cs.cmu.edu}}), or Zi
Yang (\href{mailto:ziy@cs.cmu.edu}{\nolinkurl{ziy@cs.cmu.edu}}).

\end{enumerate}

\end{minipage}
\hspace{-0.1\textwidth}

\end{titlingpage}

\input{uima/cpe}
\input{uima/as}

%\input{appendix/intro}

\end{document}
