% 
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0
% Unported License. To view a copy of this license, visit
% http://creativecommons.org/licenses/by-sa/3.0/.
%
% author: Zi Yang <ziy@cs.cmu.edu>, Di Wang <diwang@cs.cmu.edu>
% date: 08/28/2013
%
\documentclass[oneside]{memoir}

\renewcommand{\chaptername}{Task}

\usepackage{times}

\usepackage{titlesec}
\titleformat{\section}{\normalfont\Large\bfseries}{Task \thesection}{1em}{}

\usepackage{url}
\usepackage{hyperref}

\usepackage{graphicx}
\graphicspath{{../../fig/git-and-maven/}}

\usepackage{listings}
\usepackage{color}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{lightblue}{rgb}{0.95,0.95,1}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\lstset{
  basicstyle=\ttfamily\small,
  numbers=left,
  numberstyle=\tiny\color{gray},
  stepnumber=2, 
  numbersep=5pt,
  backgroundcolor=\color{lightblue},
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  frame=lines,
  rulecolor=\color{black},
  tabsize=2,
  captionpos=b,
  breaklines=true,
  breakatwhitespace=false,
  title=\lstname,
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  escapeinside={\%*}{*)},
  morekeywords={*,...},
}
\usepackage{letltxmacro}
\makeatletter
\LetLtxMacro\@@lst@inputlisting\lst@inputlisting
\renewcommand\lst@inputlisting[2][]{%
  \try@listingspath{#2}%
  \if@tempswa
    \typeout{Using \@foundlisting}%
    \@@lst@inputlisting[#1]{\@foundlisting}%
  \else
    \typeout{Missing file #2}\endgroup
  \fi}
\def\listingspath#1{\def\@listingspath{#1}}
\listingspath{}
\def\try@listingspath#1{%
  \@tempswafalse
  \expandafter\@tfor\expandafter\next
  \expandafter:\expandafter=\@listingspath\do
  {\if@tempswa\@break@tfor\fi
   \IfFileExists{\next/#1}{\@tempswatrue\xdef\@foundlisting{\next/#1}}{}}%
}
\makeatletter
\listingspath{{../../lst/git-and-maven/}}

\definecolor{shadecolor}{gray}{0.9}

\newenvironment{qa}
{\begin{shaded}\begin{itemize}}
{\end{itemize}\end{shaded}}

\title{{\bfseries 11-791 Design and Engineering of Intelligent Information
System \& \\11-693 Software Methods for Biotechnology \\Homework 0}\\
\vspace{1em}
\itshape\rmfamily Software installation, configuration, and your first Maven
project hosted on GitHub}

\date{}

\begin{document}

\begin{titlingpage}
\maketitle

\hspace{-0.1\textwidth}
\begin{minipage}{1.2\textwidth}
\vspace{-5em}
\textbf{Important dates}
\begin{itemize}

\item \textbf{Hand out: August 28.}

\item \textbf{Turn in: September 4.} A bash script will automatically collect
your submissions and execute your latest release (e.g., hw0-ID-0.0.1.jar) on our
maven repository. The output from your jar will be compared with our expected
output. Simply copy the code from the guideline will do the work!
\end{itemize}

\textbf{Useful information}
\begin{enumerate}
\item We suggest you to start Homework 0 as early as possible.

\item As you'll see at the beginning of Task 2, that installation of the same
software on different platforms differs a lot, we have thus created three forums
for you to discuss Windows/Linux/Mac platform related issues. We will try our
best to help you solve whatever problems you might have, but we also encourage
you, the experts in any of these platforms, to work with us to answer the
questions from your classmates. You can find the discussion boards at
\url{http://blackboard.andrew.cmu.edu}. Plus, you might find Google is also a
good place to raise your concerns and find answers.

\item For any question regarding Homework 0, please send us mails to, Alkesh
Patel
(\href{mailto:alkeshku@andrew.cmu.edu}{\nolinkurl{alkeshku@andrew.cmu.edu}}), Di
Wang (\href{mailto:diwang@cs.cmu.edu}{\nolinkurl{diwang@cs.cmu.edu}}), or Zi
Yang (\href{mailto:ziy@cs.cmu.edu}{\nolinkurl{ziy@cs.cmu.edu}}).

\item Both source files and derived pdf file of this tutorial are publicly
available (yes, \emph{open source}!) on GitHub

\url{http://github.com/ziy/software-engineering-preliminary}

which means if you find any errors or easier ways to achieve the same goal,
please feel free to fork the project and send a pull request back to me. Once
your request is confirmed, a newer version will come out immediately to help
other students! Or you can just report an issue at

\url{http://github.com/ziy/software-engineering-preliminary/issues}

\end{enumerate}

\end{minipage}
\hspace{-0.1\textwidth}
\end{titlingpage}

\input{account/intro}

\input{config/intro}

\input{project/intro}

\end{document}
